\textbf{ Spectrophotometric parallaxes with linear models:\\ Accurate distances for luminous red-giant stars }

### 2018-10-17 paper/sp.tex
table

In the end, this method produces a spectrophotometric parallax estimate $\sparallax_m$
and uncertainty $\ssigma_m$ for every star $m$.
\tablename~\ref{tab:output} shows a snippet of this output, with the full output available
as an electronic data table associated with this \documentname.
In order to use this output with \gaia\ astrometry, we recommend joining the table to the
\gaia\ Catalog on the \zmass\ ID (name), as per the instructions at the \gaia\ Archive (\citealt{gaiaarchive}).
In order to use this output with \apogee\ radial velocities and element abundances, we recommend
joining the table to the \sdssiv\ Catalog on the \zmass\ ID (name).
\begin{table}
\caption{HOGG and ACE TBD: The generated spectrophotometric parallaxes.
This table is just a snippet; the full table is available online (HOGG HOW?)\label{tab:output}}
\end{table}

>>>>

In the end, this method produces a spectrophotometric parallax estimate $\sparallax_m$
and uncertainty $\ssigma_m$ for every star $m$.
\tablename~\ref{tab:output} shows a snippet of this output, with the full output available
as an electronic data table associated with this \documentname.
In order to use this output with \gaia\ astrometry, we recommend joining the table to the
\gaia\ Catalog on the \zmass\ ID (name), as per the instructions at the \gaia\ Archive (\citealt{gaiaarchive}).
In order to use this output with \apogee\ radial velocities and element abundances, we recommend
joining the table to the \sdssiv\ Catalog on the \zmass\ ID (name).

\newpage
\begin{longrotatetable}
\startlongtable
\begin{deluxetable*}{ccccccc}
\tablecaption{HOGG and ACE TBD: The generated spectrophotometric parallaxes.
This table is just a snippet; the full table is available online (HOGG HOW?)\label{tab:output}}
\tablehead{\dcolhead{\texttt{2MASS\_ID}} & \dcolhead{\texttt{Gaia\_parallax}} & \dcolhead{\texttt{Gaia\_parallax\_err}} & \dcolhead{\texttt{spec\_parallax}} & \dcolhead{\texttt{spec\_parallax\_err}} & \dcolhead{\texttt{training\_set}} & \dcolhead{\texttt{sample}}}
\startdata
2M00000002+7417074 & 0.3191313429473075 & 0.032948037183877704 & 0.31849999096965226 & 0.01643285514291281 & 0 & B \\
2M00000317+5821383 & 0.3643040248194837 & 0.05099089240834289 & 0.4428242906062965 & 0.01834130205824606 & 0 & A \\
2M00000546+6152107 & 0.3154104939032093 & 0.035141087048246 & 0.3292112764247769 & 0.016388459680198957 & 0 & B \\
2M00000797+6436119 & 0.07711986267105561 & 0.08408755179430512 & 0.19428078181594394 & 0.019370065406281896 & 1 & B \\
2M00001719+6221324 & 0.13952084276830487 & 0.04389977390011321 & 0.1563998166245657 & 0.012831080487863935 & 0 & B \\
2M00002005+5703467 & 0.3003205275388493 & 0.024656309709138968 & 0.2372046982030924 & 0.020327826647521956 & 0 & B \\
2M00002036+6153416 & 0.06569746266321969 & 0.0636606119367412 & 0.1347406498933188 & 0.013122259531649945 & 1 & A \\
2M00002118+6136420 & 0.19358517288879123 & 0.03229292271974642 & 0.2172989314297034 & 0.013278872163629496 & 1 & B \\
2M00002227+6223341 & 0.1965229567661197 & 0.04503624629849183 & 0.1461267214260898 & 0.008928599127162944 & 0 & B \\
2M00002472+5518473 & 0.09468551608472082 & 0.020679980798059373 & 0.14731238757486897 & 0.009570425952478014 & 1 & B \\
2M00002908+6140446 & 0.16751577398691722 & 0.04602771820716873 & 0.19135489809281317 & 0.01758606714554385 & 1 & A \\
2M00003061+5820590 & 0.16692055579543114 & 0.03394660614876257 & 0.35023347779063707 & 0.029004068376645976 & 1 & A \\
... & ... & ... & ... & ... & ... & ...  \\
 \enddata
\tablecomments{Columns show...}
\end{deluxetable*}
\end{longrotatetable}
\newpage
